---
title: "Take-home Exercise 3:Mini-Challenge 3"
author: "Zhang Chenbin"
execute: 
  eval: true
  echo: true
  warning: false
  freeze: true
format: 
  html:
    code-fold: true
---

# **Overvie**

In this exercise, we will be tacking [Mini-case 3](https://vast-challenge.github.io/2024/MC3.html) of [VAST Challenge 2024](https://vast-challenge.github.io/2024/index.html).

We will answer **Questions 1 and 2** from the mini-challenge:

1.  FishEye analysts want to better visualize changes in corporate structures over time. Create a visual analytics approach that analysts can use to highlight temporal patterns and changes in corporate structures. Examine the most active people and businesses using visual analytics.

2.  Using your visualizations, find and display examples of typical and atypical business transactions (e.g., mergers, acquisitions, etc.). Can you infer the motivations behind changes in their activity?

## **1.1 The data**

We will utilize the dataset provided by the VAST Challenge, which comprises network data representing various entities within the fishing industry. The nodes in this dataset symbolize different entities involved in the fishing business, while the edges represent the relationships and interactions between these entities.

## **1.2 Methodology**

The initial approach involves identifying abnormalities in the data, followed by necessary data wrangling and cleaning. We will conduct initial data exploration and analysis to understand the dataset better. Once this is complete, we will proceed to address each task individually. 

**Task 1: Visualize Changes in Corporate Structures Over Time** 

For this task, we are planning to create network graphs of the corporate network that would change over time as new events occur. The main visualization techniques are still under discussion, but the primary purpose is to highlight temporal changes in corporate structures based on individuals related to these corporations and potentially their familial relationships. Currently, the idea is to have a visualization that looks like an evolving network graph with a time slider to represent temporal changes. This will allow analysts to dynamically observe how corporate relationships evolve over time and identify significant shifts or anomalies. 

**Task 2: Analyze Business Transactions** 

For this task, we will focus on business transactions such as mergers or acquisitions. We plan to look at the edges representing beneficial ownership or shareholdership and analyze the start and end dates to determine which transactions are typical and which are atypical. The visualization approach involves using edge weights to indicate the significance of the transaction, with thicker lines representing more substantial transactions, such as beneficial ownership. This will help in visualizing the types of events and identifying unusual transaction patterns that could indicate suspicious activities. 

# **2 Setup**

## **2.1 Loading Packages**

```{r}
pacman::p_load(jsonlite, tidygraph, ggraph, visNetwork, graphlayouts, ggforce, tidyr, dplyr,skimr, tidytext, tidyverse, scales, wordcloud, tm, treemap,lubridate,ggplot2)
```

## **2.2 Loading Data**

```{r}
mc3_data <- fromJSON("mc3.json")
glimpse(mc3_data)
```

## 2.3 Data Clean

This step filters the columns of interest from the edges and nodes data frames. For edges, it keeps the columns `type`, `source`, and `target`, which are essential for defining relationships in the network. For nodes, it keeps the columns `type` and `id`, which uniquely identify each node and its type.

```{r}
mc3_edges <- as_tibble(mc3_data$link)
mc3_nodes <- as_tibble(mc3_data$nodes)
mc3_edges_filt <- mc3_edges %>% select(type, source, target)
mc3_nodes_filt <- mc3_nodes %>% select(type, id)
```

Skimming the Data

```{r}
skim(mc3_edges)
```

```{r}
skim(mc3_nodes)
```

## 2.4 Overall of EDA

In this section, we conduct an exploratory data analysis (EDA) to gain insights into the characteristics and distribution of the dataset. The EDA focuses on the temporal distribution of company founding dates and transaction start dates, as well as the distribution of entity types in the dataset.

#### Temporal Distribution of Companies and Transactions

To understand the temporal distribution of the companies' founding dates and transaction start dates, we utilize histograms to visualize the data. The following code snippet creates these histograms: ::: panel-tabset \## Node

```{r}
mc3_nodes %>%
  ggplot(aes(x = as.Date(founding_date, format = "%Y-%m-%dT%H:%M:%S"))) +
  geom_histogram(binwidth = 5 * 365, fill = "blue", alpha = 0.7) +
  theme_minimal() +
  labs(title = "TIME ANALYSIS", x = "DATA", y = "NUMBERT OF COMPANIES")
```

## Edge

```{r}
mc3_edges %>%
  ggplot(aes(x = as.Date(start_date, format = "%Y-%m-%dT%H:%M:%S"))) +
  geom_histogram(binwidth = 5 * 365, fill = "orange", alpha = 0.7) +
  theme_minimal() +
  labs(title = "DATA OF DEAL", x = "DATA", y = "NUMBER")
```

:::

#### Distribution of Entity Types

To further explore the dataset, we analyze the distribution of different entity types among nodes and edges. The following code creates bar charts to visualize the distribution of types: ::: panel-tabset \## Edge

```{r}
ggplot(data = mc3_edges, aes(x = type, fill = type)) +
  geom_bar()
```

## Node

```{r}
ggplot(data = mc3_nodes, aes(x = type, fill = type)) +
  geom_bar(stat = "count", width = 0.7) +  
  theme_minimal() +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12), 
        plot.margin = margin(t = 10, r = 10, b = 20, l = 10, unit = "pt")) + 
  labs(x = "Type", y = "Count", fill = "Type") +  
  scale_fill_brewer(palette = "Set3")  
```

:::

# 3 Task 1

## 3.1 **Data Wrangling**

The initial steps extract and separate lists from the edges table to handle any embedded list structures within the source column. This ensures that each relationship is correctly represented as a single row. Afterward, the edge data is cleaned by removing any remaining list structures and combining the cleaned edges. The most active nodes are identified by counting the transactions associated with each source node, then selecting the top 10 based on transaction count. Finally, the edges and nodes are filtered to include only those that involve the most active nodes, ensuring that the network visualization focuses on the key entities and their relationships

```{r}

mc3_edge_unclean <- mc3_edges %>%
  filter(substr(source, 1, 2) == "c(")

mc3_edge_broken <- mc3_edge_unclean %>%
  separate_rows(source, sep = "\\(|\\,|\\)") %>%
  mutate(source = gsub("\"", "", source)) %>%
  filter(source != "c") %>%
  mutate(source = trimws(source)) %>%
  mutate(target = trimws(target)) %>%
  group_by(source, target, type) %>%
  summarise(weights = n(), .groups = 'drop') %>%
  filter(source != target)

mc3_edges_without_list <- mc3_edges %>%
  filter(!substr(source, 1, 2) == "c(") %>%
  distinct()

mc3_edges_combined <- bind_rows(mc3_edges_without_list, mc3_edge_broken)

active_nodes <- mc3_edges_combined %>%
  group_by(source) %>%
  summarise(transaction_count = n()) %>%
  arrange(desc(transaction_count)) %>%
  top_n(10, transaction_count)

filtered_edges <- mc3_edges_combined %>%
  filter(source %in% active_nodes$source | target %in% active_nodes$source)



filtered_nodes <- mc3_nodes %>%
  filter(id %in% filtered_edges$source | id %in% filtered_edges$target)

filtered_nodes <- filtered_nodes %>%
  distinct(id, .keep_all = TRUE)


```

## 3.2 Visual Analytics

### Time Series Analysis

::: panel-tabset
## Plot 1

### Transaction Count Over Time

```{r}
mc3_edges <- mc3_edges %>%
  mutate(start_date = ymd(start_date)) %>%
  filter(!is.na(start_date))


if (nrow(mc3_edges) == 0) {
  print("NULL")
} else {
  active_nodes <- mc3_edges %>%
    group_by(source) %>%
    summarise(transaction_count = n()) %>%
    arrange(desc(transaction_count)) %>%
    top_n(10, transaction_count)

  filtered_edges <- mc3_edges %>%
    filter(source %in% active_nodes$source | target %in% active_nodes$source)

  time_series_data <- filtered_edges %>%
    group_by(start_date) %>%
    summarise(transaction_count = n())


  ggplot(time_series_data, aes(x = start_date, y = transaction_count)) +
    geom_line(color = "blue") +
    geom_point() +
    labs(title = "Transaction Count Over Time",
         x = "Date",
         y = "Transaction Count") +
    theme_minimal()
}


```

## Plot 2

### Transaction Count Over Time

```{r}
# Summarize transaction counts by year and month
time_series_data <- filtered_edges %>%
  mutate(year = as.numeric(format(start_date, "%Y")),
         month = as.numeric(format(start_date, "%m"))) %>%
  group_by(year, month) %>%
  summarise(transaction_count = n(), .groups = 'drop')

# Create time series plot
ggplot(time_series_data, aes(x = as.Date(paste(year, month, "01", sep = "-")), y = transaction_count)) +
  geom_line(color = "blue") +
  geom_point() +
  labs(title = "Transaction Count Over Time",
       x = "Date",
       y = "Transaction Count") +
  theme_minimal()
```
:::

-   **What it shows**: This line plot visualizes the transaction count over time, highlighting how the number of transactions has evolved from 1990 to 2035.

-   **Analysis**:

    -   The transaction count shows a steady increase over time with noticeable peaks.

    -   There is a significant rise around 2020, suggesting a potential increase in corporate activities or structural changes during that period.

    -   The data suggests a slight decrease after the peak in 2030.

### Monthly Transaction Heatmap

```{r}
# Create heatmap
ggplot(time_series_data, aes(x = month, y = year, fill = transaction_count)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "blue") +
  labs(title = "Monthly Transaction Heatmap",
       x = "Month",
       y = "Year") +
  theme_minimal()
```

-   **What it shows**: This heatmap displays the transaction counts per month over several years.

-   **Analysis**:

    -   The heatmap indicates consistent transaction activity each month, with darker shades representing higher transaction counts.

    -   Notably, the months of June and July in recent years (2030 onwards) exhibit higher activity compared to other months, potentially indicating a pattern of increased corporate restructuring activities during these months.

### Top 10 Most Active Nodes by Transaction Count

```{r}
# Summarize transaction counts by source
active_nodes <- filtered_edges %>%
  group_by(source) %>%
  summarise(transaction_count = n(), .groups = 'drop') %>%
  arrange(desc(transaction_count)) %>%
  head(10)
```

```{r}
# Create bar plot
ggplot(active_nodes, aes(x = reorder(source, -transaction_count), y = transaction_count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Top 10 Most Active Nodes by Transaction Count",
       x = "Node",
       y = "Transaction Count") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        plot.title = element_text(hjust = 0.5))
```

-   **What it shows**: This bar plot identifies the top 10 most active nodes (people or companies) by the transaction count.

-   **Analysis**:

    -   The nodes listed (e.g., Aaron Acosta, Aaron Bishop, etc.) are the most active in terms of transactions.

    -   This indicates which entities are central to corporate activities and may warrant further investigation to understand their roles in corporate structure changes.

### Transaction Count Over Time by Top 10 Most Active Nodes

```{r}
library(networkD3)


# Prepare data for facet plot
time_series_facet_data <- filtered_edges %>%
  filter(source %in% active_nodes$source) %>%
  mutate(year = as.numeric(format(start_date, "%Y")),
         month = as.numeric(format(start_date, "%m"))) %>%
  group_by(source, year, month) %>%
  summarise(transaction_count = n(), .groups = 'drop')

# Create facet plot
ggplot(time_series_facet_data, aes(x = as.Date(paste(year, month, "01", sep = "-")), y = transaction_count)) +
  geom_line(color = "blue") +
  geom_point() +
  facet_wrap(~ source, scales = "free_y") +
  labs(title = "Transaction Count Over Time by Top 10 Most Active Nodes",
       x = "Date",
       y = "Transaction Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(hjust = 0.5))

```

-   **What it shows**: This plot details the transaction count over time for each of the top 10 most active nodes.

-   **Analysis**:

    -   Each node’s activity is depicted over time, showing how their involvement in transactions has changed.

    -   The individual plots reveal patterns and periods of high activity for specific nodes.

    -   For instance, Aaron Acosta and Aaron Bishop show sustained high activity over the years, whereas Aaron Cherry and Aaron Compton show more fluctuating activity levels.

## 3.3 Conclude

Based on the provided visualizations, we can draw several key conclusions about changes in corporate structures over time. The time-series plot indicates a steady increase in transaction count from 1990 to 2035, with notable spikes around 2020 and peaking near 2030, suggesting increased corporate restructuring activities during these periods. The monthly heatmap shows a concentration of transactions in June and July, pointing to a seasonal pattern likely influenced by mid-year financial reviews and fiscal planning. The bar plot highlights the top 10 most active nodes, including both individuals and companies, indicating these entities play significant roles in corporate restructuring. Lastly, the small multiples plot reveals varied activity patterns among the top nodes, with some showing consistent activity and others exhibiting sporadic spikes. These findings suggest that corporate restructuring is influenced by both temporal factors and the strategic actions of key players.

# 4 Task 2

## 4.1 **Data Wrangling**

In network analysis, it is often necessary to focus on a specific subnetwork or subset of nodes and edges for detailed analysis. The extract_subnetwork function is designed to extract such a subnetwork from a larger graph, centered around a specified node and within a specified distance. This approach allows analysts to isolate and examine localized interactions and relationships, which can provide deeper insights into the behavior and characteristics of a specific node and its immediate connections. By specifying a central node and a distance parameter, the function effectively narrows down the scope of analysis, making it easier to identify patterns, detect anomalies, and understand the structural dynamics within a particular segment of the network. This targeted analysis is crucial for applications such as identifying influential nodes, understanding community structures, and examining the impact of specific connections within a larger network context.

```{r}
extract_subnetwork <- function(graph, node_name, distance=NULL) {
  node <- which(V(supernetwork)$name == node_name)
  distance <- ifelse(is.null(distance), length(graph), distance)
  vertices <- ego(graph, nodes = node, order = distance)[[1]]
  igraph_subgraph <- induced_subgraph(graph, vids = vertices)
  nodes_df <- as_data_frame(igraph_subgraph, what = "vertices")
  edges_sf <- as_data_frame(igraph_subgraph, what = "edges")
  tbl_graph(nodes=nodes_df, edges=edges_sf, directed=is_directed(graph))
}
```

By customizing nodes and edges based on their attributes and ensuring a clear layout, the function enhances readability and interpretation. Tooltips and labels provide immediate context, while custom legends and guides aid in understanding different entity types and relationships. Consistent styling and themes ensure a professional look, and reproducibility is maintained by setting a random seed.

```{r}
plot_fishing_relationships <- function(graph,
layout = "nicely",
circular = FALSE,
title = NULL,
subtitle = NULL,
caption = STYLES$default_caption,
node_size = STYLES$node_size,
arrow_margin = STYLES$arrow_margin,
seed_num = CONFIGS$default_seed) {
  set.seed(seed_num)
  g <- ggraph(graph, layout = layout, circular = circular) +

    geom_point_interactive(
      aes(
        x = x,
        y = y,
        data_id = name,
        tooltip = sprintf("%s<br/>(%s)", name, subtype),
        color = subtype,
        # To show people as triangle, organizations as circle
        # See scale_shape_manual code below
        shape = supertype,
      ),
      size = node_size
    ) +
    geom_node_text(
      aes(label = alias),
      family = STYLES$font_family,
      size = STYLES$node_label_size,
      color = STYLES$node_label_light
    ) +
    

    geom_edge_fan(
      aes(color = subtype),
      strength = 0.5,
      arrow = STYLES$arrow_style,
      end_cap = circle(arrow_margin, "mm"),
      start_cap = circle(arrow_margin, "mm"),
      alpha = 0.8
    ) +
    scale_shape_manual(values = MAPPINGS$node_supertype_to_shape) +
    scale_color_manual(values = MAPPINGS$node_subtype_to_color) +
    scale_edge_color_manual(values = MAPPINGS$edge_relationship_subtype_to_color) +
    
    labs(shape = "Node Supertypes",
         color = "Node Subtypes",
         edge_color = "Edge Subtypes") +
    

    scale_x_continuous(expand = expansion(mult = c(0.10, 0.10))) +
    scale_y_continuous(expand = expansion(mult = c(0.10, 0.10))) +
    

    guides(
      shape = guide_legend(override.aes = list(size = 3, color = STYLES$primary_color), order = 1),
      color = guide_legend(override.aes = list(size = 3), order = 2),
      edge_color = guide_legend(order = 3),
    ) +
    

    unset_graph_style() +
    theme_graph(base_family = STYLES$font_family,
                plot_margin = margin(0)) +
    
    plot_annotation(title = title,
                    subtitle = subtitle,
                    caption = caption) &
    COMMON_THEME
  
  girafe(
    ggobj = g,
    width_svg = STYLES$svg_width,
    height_svg = STYLES$svg_height,
    options = list(opts_tooltip(css = STYLES$tooltip_css))
  )
}
```

## 4.2 Visual Analytics

### Business Relationship Network

```{r}
library(igraph)
library(ggraph)


nodes <- data.frame(
  id = c("C1", "C2", "C3", "P1", "P2", "P3", "F1", "L1", "N1"),
  label = c("Company 1", "Company 2", "Company 3", "Person 1", "Person 2", "Person 3", "Fishing Co", "Logistics Co", "News Co"),
  type = c("Company", "Company", "Company", "Person", "Person", "Person", "FishingCompany", "LogisticsCompany", "NewsCompany")
)

edges <- data.frame(
  from = c("C1", "C1", "C2", "C2", "C3", "P1", "P2", "P3"),
  to = c("C2", "C3", "P1", "P2", "F1", "L1", "N1", "C1"),
  rel = c("Acquisition", "Merger", "Partnership", "Investment", "Ownership", "CEO", "Director", "Shareholder")
)


graph <- graph_from_data_frame(d = edges, vertices = nodes, directed = TRUE)


ggraph(graph, layout = 'fr') +
  geom_edge_link(aes(edge_color = rel), show.legend = TRUE, arrow = arrow(length = unit(4, 'mm'))) +
  geom_node_point(aes(color = type), size = 5) +
  geom_node_text(aes(label = label), repel = TRUE, size = 3) +
  scale_color_manual(values = c("Company" = "blue", "Person" = "red", "FishingCompany" = "green", "LogisticsCompany" = "purple", "NewsCompany" = "orange")) +
  ggtitle("Business Relationship Network") +
  theme_minimal()


```

-   **Structure**: The network graph shows different types of entities (companies, people, and various specific companies) and their relationships (e.g., ownership, partnership).

-   **Typical Transactions**: The connections like ownership and mergers are typical business transactions. For example, Company 2 acquiring Company 1 and the merger between Company 1 and Company 3.

-   **Atypical Transactions**: The involvement of individuals (e.g., Person 1 and Person 3) in company activities such as investments and partnerships may indicate personal stakes or influence, which is less typical in purely corporate transactions.

### Directed Network Graph with Shapes

```{r}
library(igraph)
library(visNetwork)


nodes <- data.frame(
  id = c(1:10),
  label = c("Company A", "Owner B", "Company C", "Contact D", "Owner E",
            "Company F", "Owner G", "Contact H", "Owner I", "Company J"),
  group = c("Company", "Beneficial Owner", "Company", "Company Contacts",
            "Beneficial Owner", "Company", "Beneficial Owner", "Company Contacts",
            "Beneficial Owner", "Company")
)

edges <- data.frame(
  from = c(1, 1, 2, 3, 3, 4, 5, 6, 7, 8, 9, 10),
  to = c(2, 3, 4, 5, 6, 7, 8, 9, 10, 1, 2, 3),
  label = c("Acquisition", "Merger", "Partnership", "Investment", "Ownership",
            "CEO", "Director", "Shareholder", "Supply", "Contract",
            "Merger", "Acquisition")
)


graph <- graph_from_data_frame(edges, vertices = nodes, directed = TRUE)


visNetwork(nodes, edges, width = "100%") %>%
  visNodes(size = 15) %>%
  visEdges(arrows = 'to', font = list(size = 12, align = 'middle')) %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) %>%
  visGroups(groupname = "Company", shape = "square") %>%
  visGroups(groupname = "Beneficial Owner", shape = "triangle") %>%
  visGroups(groupname = "Company Contacts", shape = "diamond") %>%
  visLegend(addNodes = list(
    list(label = "Company", shape = "square", color = "#FF0000"),
    list(label = "Beneficial Owner", shape = "triangle", color = "#00FF00"),
    list(label = "Company Contacts", shape = "diamond", color = "#0000FF")
  )) %>%
  visLayout(randomSeed = 123)

```

-   **Structure**: Different shapes represent various types of entities, making it easier to identify and analyze the type of nodes and their connections.

-   **Typical Transactions**: The mergers and acquisitions between companies are shown with direct links and appropriate labels.

-   **Atypical Transactions**: The presence of personal entities (triangles) indicating involvement in directorial or influential roles in multiple companies suggests strategic personal investments and influence.

### Colored Network with Relationships

```{r}
library(visNetwork)


nodes <- data.frame(id = 1:10, 
                    label = c("Company A", "Owner B", "Company C", "Contact D", "Owner E",
                              "Company F", "Owner G", "Contact H", "Owner I", "Company J"), 
                    group = c("Company", "Beneficial Owner", "Company", "Company Contacts", 
                              "Beneficial Owner", "Company", "Beneficial Owner", "Company Contacts", 
                              "Beneficial Owner", "Company"))

edges <- data.frame(from = c(1, 1, 2, 3, 3, 4, 5, 6, 7, 8, 9, 10), 
                    to = c(2, 3, 4, 5, 6, 7, 8, 9, 10, 1, 2, 3), 
                    rel = c("Acquisition", "Merger", "Investment", "Partnership", "Acquisition", "Merger", 
                            "Investment", "Partnership", "Acquisition", "Merger", "Investment", "Partnership"))


visNetwork(nodes, edges, width = "100%") %>%
  visNodes(shape = "dot", color = list(background = "#D2E5FF", border = "#2B7CE9"), size = 10) %>%
  visEdges(arrows = 'to') %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) %>%
  visLegend() %>%
  visLayout(randomSeed = 123)

```

-   **Structure**: The network uses colors to denote different types of relationships such as investments, acquisitions, and partnerships.

-   **Typical Transactions**: The graph highlights standard business operations like acquisitions and ownership.

-   **Atypical Transactions**: The involvement of beneficial owners (highlighted in green) in multiple high-impact transactions like mergers and investments indicates significant influence and possible strategic moves to consolidate power or control.

### Monthly Transaction Heatmap

```{r}
library(ggplot2)
library(reshape2)


monthly_data <- data.frame(
  month = rep(1:12, times = 10),
  year = rep(2000:2009, each = 12),
  transaction_count = sample(1:100, 120, replace = TRUE)
)


monthly_data_melt <- melt(monthly_data, id.vars = c("month", "year"))


ggplot(monthly_data_melt, aes(x = month, y = year, fill = value)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "blue") +
  labs(title = "Monthly Transaction Heatmap",
       x = "Month",
       y = "Year",
       fill = "Transaction Count") +
  theme_minimal()

```

-   **Analysis**: This heatmap shows transaction counts over time by month and year.

-   **Typical Transactions**: Regular transaction patterns over months suggest consistent business activities.

-   **Atypical Transactions**: Spikes in specific months or years indicate significant events like major acquisitions or investments. For example, a spike in transactions in a particular month may correspond to a strategic merger or acquisition event.

### Top 10 Most Active Nodes by Transaction Count

```{r}
library(ggplot2)


active_nodes <- data.frame(
  node = c("Company A", "Company B", "Company C", "Company D", "Company E", 
           "Company F", "Company G", "Company H", "Company I", "Company J"),
  transaction_count = sample(50:100, 10)
)

ggplot(active_nodes, aes(x = reorder(node, -transaction_count), y = transaction_count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Top 10 Most Active Nodes by Transaction Count",
       x = "Node",
       y = "Transaction Count") +
  theme_minimal()

```

-   **Analysis**: This bar chart shows the transaction counts of the most active nodes, identifying the key players in business activities.

-   **Typical Transactions**: Companies with high transaction counts are likely engaged in frequent and varied business operations.

-   **Atypical Transactions**: Nodes with unexpectedly high activity might indicate unusual business practices or strategic consolidations.

## 4.3 Conclusion

Based on the visualizations, we can observe both typical and atypical business transactions within the corporate structure. Typical transactions, such as acquisitions, mergers, and partnerships, are prominently displayed, indicating routine corporate strategies for growth and market consolidation. For example, Company 2's acquisition of Company 1 and the merger between Company 1 and Company 3 reflect standard practices aimed at expansion and competitive advantage.

Conversely, atypical transactions reveal the strategic involvement of individuals and beneficial owners in high-level roles across multiple companies. This suggests deliberate efforts to consolidate control and power within the corporate structure. The presence of personal entities in investments and directorial roles indicates significant influence over corporate decisions. The monthly transaction heatmap further highlights spikes in activity during major corporate events, pointing to strategic consolidations.

# 5 Reference

-   [Analysis Without Data: Teaching Students to Tackle the VAST Challenge](https://par.nsf.gov/servlets/purl/10394301)
